---
title: "Untitled"
output: html_document
---

# Breeding success of Bonelli’s eagle is directly and indirectly impacted by movement

## Effect of intrinsic and extrinsic factors on breeding success 
We studied three breeding parameters to gain a better understanding of the breeding success of Bonelli’s eagle:  
 - breeding probability (pair having laid among the pairs present on a breeding site), 
 - hatching success (pair having at least one hatching among the pairs having laid eggs)
 - fledging success (pair having fledged at least one young among pairs having hatched at least one egg). 
 
We fitted generalized linear mixed models (GLMM) with a binomial distribution for all breeding parameters to model the relationship between the breeding parameters with intrinsic factors (recruitment) and local weather variables (rainfall, temperature and wind).

We included a random effect for the breeding site to consider inter-breeding site heterogeneity and repeated measurements. 

For each breeding parameter, we chose to study the effects of weather conditions only during the period preceding the event (weather conditions during pre-breeding for breeding probability, during incubation for hatching success, and during rearing for fledging success). 

# Packages and fonctions
```{r}
library(ggplot2); library(patchwork)

#### Function to plot predict of LMM models for continuous variables
plot_predict<-function(var_x_chara, var_x, model, title, x_lab, y_lab, col){
  
   df <- ggeffects::ggpredict(model, terms = c(var_x_chara), ci.lvl = 0.95, back.transform = TRUE)
  
  mean=mean(var_x)
  sd=sd(var_x)
  
  df$x_unscale<-(df$x * sd) + mean
  
  ggplot(df, aes(x_unscale, predicted)) + 
    geom_line(aes(), color=col) +
    geom_ribbon(aes(ymin=conf.low, ymax=conf.high), alpha=0.5, fill=c(col))+
    geom_rug(aes(x_unscale, predicted))+
    ggtitle(title)+
    xlab(x_lab)+
    ylab(y_lab)+
    theme_minimal()
}

#### Function to plot predict of LMM models for qualitative variables
plot_quali<-function(model, terms, title, y_lab, x_lab, color){
  
  df <- ggeffects::ggpredict(model, terms = c(terms), ci.lvl = 0.95, back.transform = TRUE)
  
  df$x<-as.factor(df$x)
  ggplot(df, aes(x, predicted, color=x)) +
    geom_point(size=3, show.legend = F)+
    geom_errorbar(aes(ymin  = conf.low, 
                      ymax = conf.high), 
                  width = .1, size=1, show.legend = F) +
    scale_color_manual(values=color)+
    ggtitle(title)+
    xlab(x_lab)+
    ylab(y_lab)+
    theme_minimal()
}

```

# Data 
Territory : breeding territory index
year : year of the breeding event 

recruitment_female : 1 if a new female have recruit on the breeding site, 0 if not
recruitment_female : 1 if a new male have recruit on the breeding site, 0 if not
Recruitment : 0 = no recruitment on the breeding site, F = recruitment of a female, M = recruitment of a male, and MF = recruitment of both individuals on a breeding site

breeding_probability : pair having laid among the pairs present on a breeding site
hatching_success : pair having at least one hatching among the pairs having laid eggs
fledging_success: pair having fledged at least one young among pairs having hatched at least one egg
productivity : number of fledging chicks

wind_b2 : number of days with wind speed below 2.5 m/s
wind_a7 : number of days with wind speed above 7.5 m/s 
rainfall : cumulative rainfall (in mm) for the period
min_T : minimum mean daily temperature observed for the period
max_T : maximum mean daily temperature observed for the period

```{r}
Breeding<-read.table(here::here(file.path("data/Data_publi", "Breeding_Bonelli.csv")), header=TRUE, sep=",")

Breeding$Site<-as.factor(Breeding$Site)
summary(Breeding)
```

### Breeding probability 
Local weather condition during the pre breeding period 
```{r}
breeding_proba <- glmmTMB::glmmTMB(breeding_proba ~ Recruitment 
                                   + scale(wind_b2_prebreeding) + scale(wind_a7_prebreeding) + scale(rainfall_prebredding) 
                                   + scale(min_T_prebreeding) + scale(max_T_prebreeding)
                                   +(1|Site), data=Breeding, family = binomial) 
                                        
summary(breeding_proba)
```

Predicts 
```{r}
A<-plot_quali(breeding_proba, "Recruitment", 
              title="Breeding probability (weather conditions during pre-breeding)", y_lab="Breeding probability",x_lab="Recruitment",
              color=c( "#00AFBB", "#440154FF", "#702963", "#d90368")) 

B<-plot_predict("wind_b2_prebreeding [all]", 
                Breeding$wind_b2_prebreeding, 
                breeding_proba, title="", x_lab=" wind <2.5 m/s", y_lab="Breeding probability", col="#702963")

C<-plot_predict("wind_a7_prebreeding [all]", 
                Breeding$wind_a7_prebreeding, 
                breeding_proba, title="", x_lab=" wind >7.5 m/s", y_lab="Breeding probability", col="#702963")

D<-plot_predict("rainfall_prebredding [all]", 
                Breeding$rainfall_prebredding, 
                breeding_proba, title="", x_lab="rainfall", y_lab="Breeding probability", col="#702963")

E<-plot_predict("min_T_prebreeding[all]", 
                Breeding$min_T_prebreeding, 
                breeding_proba, title="", x_lab=" minimum Temperature", y_lab="Breeding probability", col="#702963")

ff<-plot_predict("max_T_prebreeding [all]", 
                Breeding$max_T_prebreeding, 
                breeding_proba, title="", x_lab=" maximum Temperature", y_lab="Breeding probability", col="#702963")

cowplot::plot_grid(A,B,C,D,E, ff,  ncol = 3, nrow = 2)

```


### Hatching success 
Local weather condition during the incubation period 

As we don't have the as we lacked events with recruitment of both male and female, recruitment will only have 3 levels (0 = no recruitment on the breeding site, F = recruitment of a female, M = recruitment of a male)

We only conserve breeding event that have lay at least an egg 
```{r}
## New data set with breeding event with a breeding probability of 1
Data_hatching <-Breeding[Breeding$breeding_proba==1,]

Data_hatching$Recruitment[Data_hatching$Recruitment=="MF"]<-NA
```

GLMM
```{r}
hatching_success <- glmmTMB::glmmTMB(hatching_success ~ Recruitment 
                                   + scale(wind_b2_incubation) + scale(wind_a7_incubation) + scale(rainfall_incubation) 
                                   + scale(min_T_incubation) + scale(max_T_incubation)
                                   +(1|Site), data=Data_hatching, family = binomial) 
                                        
summary(hatching_success)
```

Predicts 
```{r}
A<-plot_quali(hatching_success, "Recruitment", 
              title="Hatching success (weather conditions during incubation)", y_lab="Hatching success",x_lab="Recruitment",
              color=c( "#00AFBB", "#440154FF", "#702963", "#d90368")) 

B<-plot_predict("wind_b2_incubation [all]", 
                Data_hatching$wind_b2_incubation, 
                hatching_success, title="", x_lab=" wind <2.5 m/s", y_lab="Hatching success", col="#702963")

C<-plot_predict("wind_a7_incubation [all]", 
                Data_hatching$wind_a7_incubation, 
                hatching_success, title="", x_lab=" wind >7.5 m/s", y_lab="Hatching success", col="#702963")

D<-plot_predict("rainfall_incubation [all]", 
                Data_hatching$rainfall_incubation, 
                hatching_success, title="", x_lab="rainfall", y_lab="Hatching success", col="#702963")

E<-plot_predict("min_T_incubation [all]", 
                Data_hatching$min_T_incubation, 
                hatching_success, title="", x_lab=" minimum Temperature", y_lab="Hatching success", col="#702963")

ff<-plot_predict("max_T_incubation [all]", 
                Data_hatching$max_T_incubation, 
                hatching_success, title="", x_lab=" maximum Temperature", y_lab="Hatching success", col="#702963")

cowplot::plot_grid(A,B,C,D,E, ff,  ncol = 3, nrow = 2)

```



### Fledging success 
Local weather condition during the rearing period 

As we don't have the as we lacked events with recruitment of both male and female, recruitment will only have 3 levels (0 = no recruitment on the breeding site, F = recruitment of a female, M = recruitment of a male)

We only conserve breeding event with a positive hatching success
```{r}
## New data set with breeding event with a breeding probability of 1
Data_fledging <-Breeding[Breeding$hatching_success==1,]

Data_fledging$Recruitment[Data_fledging$Recruitment=="MF"]<-NA
```

GLMM
```{r}
fledging_success <- glmmTMB::glmmTMB(fledging_success ~ Recruitment 
                                   + scale(wind_b2_rearing) + scale(wind_a7_rearing) + scale(rainfall_rearing) 
                                   + scale(min_T_rearing) + scale(max_T_rearing)
                                   +(1|Site), data=Data_fledging, family = binomial) 
                                        
summary(fledging_success)
```

Predicts 
```{r}
A<-plot_quali(fledging_success, "Recruitment", 
              title="Fledging success (weather conditions during rearing)", y_lab="Hatching success",x_lab="Recruitment",
              color=c( "#00AFBB", "#440154FF", "#702963", "#d90368")) 

B<-plot_predict("wind_b2_rearing [all]", 
                Data_fledging$wind_b2_rearing, 
                fledging_success, title="", x_lab=" wind <2.5 m/s", y_lab="Hatching success", col="#702963")

C<-plot_predict("wind_a7_rearing [all]", 
                Data_fledging$wind_a7_rearing, 
                fledging_success, title="", x_lab=" wind >7.5 m/s", y_lab="Hatching success", col="#702963")

D<-plot_predict("rainfall_rearing [all]", 
                Data_fledging$rainfall_rearing, 
               fledging_success, title="", x_lab="rainfall", y_lab="Hatching success", col="#702963")

E<-plot_predict("min_T_rearing [all]", 
                Data_fledging$min_T_rearing, 
                fledging_success, title="", x_lab=" minimum Temperature", y_lab="Hatching success", col="#702963")

ff<-plot_predict("max_T_rearing [all]", 
                Data_fledging$max_T_rearing, 
                fledging_success, title="", x_lab=" maximum Temperature", y_lab="Hatching success", col="#702963")

cowplot::plot_grid(A,B,C,D,E, ff,  ncol = 3, nrow = 2)

```





