---
title: ''
output: html_document
---

# Breeding success of Bonelli’s eagle is directly and indirectly impacted by movement

## Relationship between movement behaviours and productivity

Effect of the three movement behaviours : 
 - proportion of time in flight
 - range of movements
  -straightness of trajectories
on the productivity, i.e. the probability of having 0, 1 or 2 chicks fledging for of Bonelli's eagle equiped with GPS (65 breeding events on 26 sites). 

To consider the hypothesis that Bonelli’s eagles show different behaviours throughout the breeding season with differences between sexes and period, we fitted several LMMs with sexes separated, and movement behaviours averaged for the pre-breeding, incubation and rearing period. 

As breeding success cannot exceed two (Bonelli’s eagles lay a maximum of two eggs), we considered an LMM with a Gaussian distribution instead of a Poisson distribution, which may produce breeding success higher than two (Mcdonald and White, 2010) . 

# Packages and fonctions
```{r}
library(ggplot2); library(patchwork)

#### Function to plot predict of LMM models

plot_predict<-function(var_x_chara, var_x, model, title, x_lab, y_lab, col){
  
  df <- ggeffects::ggpredict(model, terms = c(var_x_chara), ci.lvl = 0.95, back.transform = TRUE)
 
  ggplot(df, aes(x, predicted)) + 
    geom_line(aes(), color=col) +
    geom_ribbon(aes(ymin=conf.low, ymax=conf.high), alpha=0.5, fill=c(col))+
    geom_rug(aes(x, predicted))+
    ggtitle(title)+
    xlab(x_lab)+
    ylab(y_lab)+
    theme_minimal()
}
```

# Data 
id : identification of the individual
sex : Male or female
Territory : breeding territory index
year : year of the breeding event 

breeding_probability : pair having laid among the pairs present on a breeding site
hatching_success : pair having at least one hatching among the pairs having laid eggs
fledging_success: pair having fledged at least one young among pairs having hatched at least one egg
productivity : number of fledging chicks

Individuals movement behaviours averaged for each breeding period (pre-breeding, incubation, rearing)
 - prop_flight : The proportion of time in flight, calculated as the number of locations in flight over the total number of GPS locations for one day. A bird was considered to be in flight when its speed exceeded 3m/sproportion of time in flight (n_flight/nobs)
 - range_movement : The range of movement, median distance between all locations recorded in a single day and the first location, presumed to be the individual’s resting point during the night. 
 - straighness_trajectories : The straightness of trajectories performed during the day (calculated with the function TrajStraighness of the package trajr, McLean and Skowron Volponi, 2018). The closer to 1, the straighter the trajectory.

```{r}
data<-read.table(here::here(file.path("data/Data_publi", "Movement_breeding_Bonelli.csv")), header=TRUE, sep=",")

summary(data)
```


# MALES 
```{r}
#Subset with only males
Data_M<-data[data$Sex=="M",]
```

## Pre-Breeding 
```{r}
PB_M<-glmmTMB::glmmTMB(productivity~
                      scale(range_movement_prebreeding) + scale(prop_flight_prebreeding) + scale(straighness_trajectories_prebreeding) 
                      + (1|id), data=Data_M, family=gaussian)
summary(PB_M)
```

## Incubation 
We only conserve individuals that have lay at least an egg (breeding probability=1)

```{r}
Data_Hatching_M<-Data_M[Data_M$breeding_proba==1,]

IN_M<-glmmTMB::glmmTMB(productivity~
                      scale(range_movement_incubation) + scale(prop_flight_incubation) + scale(straighness_trajectories_incubation) 
                      + (1|id), data=Data_Hatching_M, family=gaussian)
summary(IN_M)
```

## Rearing 
We only conserve breeding event with a positive hatching success
```{r}
Data_fledging_M<-Data_Hatching_M[Data_Hatching_M$hatching_success==1,]

R_M<-glmmTMB::glmmTMB(productivity~
                      scale(range_movement_rearing) + scale(prop_flight_rearing) + scale(straighness_trajectories_rearing) 
                      + (1|id), data=Data_fledging_M, family=gaussian)
summary(R_M)
```

Predicts 
```{r}
#Pre breeding
PB_A<-plot_predict("range_movement_prebreeding", Data_M$range_movement_prebreeding, 
                PB_M, title="Pre Breeding - Males", x_lab="Range of movement", y_lab="Productivity", col="#26828EFF")
  
PB_B<-plot_predict("prop_flight_prebreeding", Data_M$prop_flight_prebreeding, 
                PB_M, title="", x_lab="% Time in flight", y_lab="Productivity", col="#26828EFF")
  
PB_C<-plot_predict("straighness_trajectories_prebreeding", Data_M$straighness_trajectories_prebreeding, 
                PB_M, title="", x_lab="Straighness of trajectories", y_lab="Productivity", col="#26828EFF")
  
#Incubation
IN_A<-plot_predict("range_movement_incubation", Data_Hatching_M$range_movement_incubation, 
                IN_M, title="Incubation - Males", x_lab="Range of movement", y_lab="Productivity", col="#26828EFF")
  
IN_B<-plot_predict("prop_flight_incubation", Data_Hatching_M$prop_flight_incubation, 
                IN_M, title="", x_lab="% Time in flight", y_lab="Productivity", col="#26828EFF")
  
IN_C<-plot_predict("straighness_trajectories_incubation", Data_Hatching_M$straighness_trajectories_incubation, 
                IN_M, title="", x_lab="Straighness of trajectories", y_lab="Productivity", col="#26828EFF")
  
#Rearing
R_A<-plot_predict("range_movement_rearing", Data_fledging_M$range_movement_rearing, 
                R_M, title="Rearing - Males", x_lab="Range of movement", y_lab="Productivity", col="#26828EFF")
  
R_B<-plot_predict("prop_flight_rearing", Data_fledging_M$prop_flight_rearing, 
                R_M, title="", x_lab="% Time in flight", y_lab="Productivity", col="#26828EFF")
  
R_C<-plot_predict("straighness_trajectories_rearing", Data_fledging_M$straighness_trajectories_rearing, 
                R_M, title="", x_lab="Straighness of trajectories", y_lab="Productivity", col="#26828EFF")

cowplot::plot_grid(PB_A, PB_B, PB_C, 
                   IN_A, IN_B, IN_C, 
                   R_A, R_B, R_C, ncol=3, nrow=3)

```

# FEMALES 
```{r}
#Subset with only females
Data_F<-data[data$Sex=="F",]
```

## Pre-Breeding 
```{r}
PB_F<-glmmTMB::glmmTMB(productivity~
                      scale(range_movement_prebreeding) + scale(prop_flight_prebreeding) + scale(straighness_trajectories_prebreeding) 
                      + (1|id), data=Data_F, family=gaussian)
summary(PB_F)
```

## Incubation 
We only conserve individuals that have lay at least an egg (breeding probability=1)

```{r}
Data_Hatching_F<-Data_F[Data_F$breeding_proba==1,]

IN_F<-glmmTMB::glmmTMB(productivity~
                      scale(range_movement_incubation) + scale(prop_flight_incubation) + scale(straighness_trajectories_incubation) 
                      + (1|id), data=Data_Hatching_F, family=gaussian)
summary(IN_F)
```

## Rearing 
We only conserve breeding event with a positive hatching success
```{r}
Data_fledging_F<-Data_Hatching_F[Data_Hatching_F$hatching_success==1,]

R_F<-glmmTMB::glmmTMB(productivity~
                      scale(range_movement_rearing) + scale(prop_flight_rearing) + scale(straighness_trajectories_rearing) 
                      + (1|id), data=Data_fledging_F, family=gaussian)
summary(R_F)
```

Predicts 
```{r}
#Pre breeding
PB_A<-plot_predict("range_movement_prebreeding", Data_F$range_movement_prebreeding, 
                PB_F, title="Pre Breeding - Females", x_lab="Range of movement", y_lab="Productivity", col="#26828EFF")
  
PB_B<-plot_predict("prop_flight_prebreeding", Data_F$prop_flight_prebreeding, 
                PB_F, title="", x_lab="% Time in flight", y_lab="Productivity", col="#26828EFF")
  
PB_C<-plot_predict("straighness_trajectories_prebreeding", Data_F$straighness_trajectories_prebreeding, 
                PB_F, title="", x_lab="Straighness of trajectories", y_lab="Productivity", col="#26828EFF")
  
#Incubation
IN_A<-plot_predict("range_movement_incubation", Data_Hatching_M$range_movement_incubation, 
                IN_F, title="Incubation - Females", x_lab="Range of movement", y_lab="Productivity", col="#26828EFF")
  
IN_B<-plot_predict("prop_flight_incubation", Data_Hatching_M$prop_flight_incubation, 
                IN_M, title="", x_lab="% Time in flight", y_lab="Productivity", col="#26828EFF")
  
IN_C<-plot_predict("straighness_trajectories_incubation", Data_Hatching_M$straighness_trajectories_incubation, 
                IN_M, title="", x_lab="Straighness of trajectories", y_lab="Productivity", col="#26828EFF")
  
#Rearing
R_A<-plot_predict("range_movement_rearing", Data_fledging_F$range_movement_rearing, 
                R_F, title="Rearing - Females", x_lab="Range of movement", y_lab="Productivity", col="#26828EFF")
  
R_B<-plot_predict("prop_flight_rearing", Data_fledging_F$prop_flight_rearing, 
                R_F, title="", x_lab="% Time in flight", y_lab="Productivity", col="#26828EFF")
  
R_C<-plot_predict("straighness_trajectories_rearing", Data_fledging_F$straighness_trajectories_rearing, 
                R_F, title="", x_lab="Straighness of trajectories", y_lab="Productivity", col="#26828EFF")

cowplot::plot_grid(PB_A, PB_B, PB_C, 
                   IN_A, IN_B, IN_C, 
                   R_A, R_B, R_C, ncol=3, nrow=3)

```







